Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-08-26 manuscript/manuscript.tex
adds MBH edits to R1

We compared the forecasting skill
\textcolor{blue}{(accuracy and precision)} of statistical and population
models based on aggregated, population-level data with the skill of
models based on individual-level data. We used a demographic dataset
that tracks the fates of individual plants from four species over 14
years to build two kinds of single-species population models,
traditional models using individual growth, survival, and recruitment
data and alternative models based on population-level (basal cover)
data. We simulated the models to answer two questions motivated by the
fact that the effects of intraspecific competition (density dependence)
and interannual weather variability act at the level of the individual
(Clark et al. 2011). First, can population models fit using aggregated
individual-level data (percent cover) adequately capture density
dependence to produce forecasts as skillful as those from models fit to
demographic data? Second, can population models fit using aggregated
data adequately capture the influence of climate on population growth
and, in turn, produce forecasts as skillful as those from models fit to
demographic data?

@@

\textcolor{blue}{Below we describe our focal plant populations, the population models we use to make predictions, and how we compare model forecasts, but offer a brief overview here.
We used two types of data: individual-level data and percent cover data.
Using the individual-level data we fit three vital rate regressions (survival, growth, and rectruitment) to build an Integral Projection Model (IPM) for simulating the plant populations.
Using the percent cover data we fit a simple, Gompertz-style population growth model, which we refer to as a quadrat-based model (QBM).
Both model types (IPM and QBM) we fit and simulate versions with and without climate covariates.
We used Bayesian ridge regression to weight the importance of each climate covariate.
We then performed cross-validation to assess each model's ability to predict out-of-sample data.
We compared the forecast accuracy ($\rho$, correlation between observations and predictions) and mean absolute error (MAE) between the IPM and the QBM to test our expectation that the IPM should outperform the QBM.
Lastly, we use in-sample forecasts to quantify each model's forecast horizon}
(Petchey et al. 2015).

@@

Our demographic data come from a northern mixed grass prairie at the
Fort Keogh Livestock and Range Research Laboratory near Miles City,
Montana, USA (\(46^{\circ}\) 19' N, \(105^{\circ}\) 48' W). The dataset
is available on Ecological Archives\footnote{\url{http://esapubs.org/archive/ecol/E092/143/}}
(Anderson et al. 2011), and interested readers should refer to the
metadata for a complete description. The site is 800 m above sea level
and mean annual precipitation (1878-2009) is 334 mm, with most annual
precipitation falling from April through September. The community is
grass-dominated, and we focused on the four most abundant grass species:
\emph{Bouteloua gracilis} (BOGR), \emph{Hesperostipa comata} (HECO),
\emph{Pascopyrum smithii} (PASM), and \emph{Poa secunda} (POSE) (Fig. 1
and Table 1). \emph{B. gracilis} is a warm-season perennial grass,
whereas \emph{H. comata}, \emph{P. smithii}, and \emph{Poa secunda} are
cool-season perennial grasses. The growing season begins in early spring
(typically in April) and lasts through mid-summer (typically in June).

From 1932 to 1945, individual plants were identified and mapped annually
in 44 1-\(\text{m}^2\) quadrats using a pantograph. The quadrats were
distributed among six pastures, each assigned a grazing treatment of
light (1.24 ha/animal unit month), moderate (0.92 ha/aum), and heavy
(0.76 ha/aum) stocking rates (two pastures per treatment). In this
analysis, we accounted for potential differences among the grazing
treatments, but do not focus on grazing\(\times\)climate interactions.
The annual maps of the quadrats were digitized and the fates of
individual plants tracked and extracted using a computer program
(Lauenroth and Adler 2008, Chu et al. 2014). The permanent quadrats have
not been relocated, but their distribution in six different pastures
means the data represent a broad spatial distribution for the study
area. Daily climate data are available for the duration of the data
collection period (1932 - 1945) from the Miles City airport, Wiley
Field, 9 km from the study site.

We modeled each grass population based on two levels of data: individual
and quadrat. The individual data are the ``raw'' data. For the
quadrat-level data we simply sum individual basal cover for each quadrat
by species. This is equivalent to a near-perfect census of quadrat
percent cover because measurement error at the individual-level is small
(Chu and Adler 2015). Based on these two datasets of 13 year-to-year
transitions, we can compare population models built using
individual-level data and aggregated, quadrat-level data. At the
individual level, we explicitly model three vital rates: growth,
survival, and recruitment. At the quadrat level, we model population
growth as change in percent cover of quadrats with non-zero cover in
year \emph{t} and in year \emph{t-1}, ignoring within-quadrat
extirpation and colonization events because they are very rare in our
time series (\(N=16\) and \(N=13\), respectively, across all species).
Sample sizes for each species and vital rate model are shown in Table 1.

@@

Our Bayesian approach to fitting the vital rate models required choosing
appropriate priors for unknown parameters and deciding which, if any, of
those priors should be hierarchical. For each species, we fit yearly
size effects and yearly intercepts hierarchically, where year-specific
coefficients were drawn from global distributions representing the mean
size effect and intercept. Quadrat random effects were also fit
hierarchically, with quadrat offsets being drawn from distributions with
mean zero and a shared variance term (independent Gaussian priors).
Climate effects were modeled as independent covariates whose prior
distributions were optimized for prediction using statistical
regularization (see \textbf{Statistical regularization: Bayesian ridge
regression} below).

All of our analyses (model fitting and simulating) were conducted in R
(R Core Team 2013). We used the `No-U-Turn' Hamiltonian Monte Carlo
sampler in Stan (Stan Development Team 2014a) to estimate the posterior
distributions of model parameters using the package \texttt{rstan} (Stan
Development Team 2014b). We obtained posterior distributions for all
model parameters from three parallel MCMC chains run for 1,000
iterations after discarding an initial 1,000 iterations. Such short MCMC
chains are possible because the Stan sampler reduces the number of
iterations needed to achieve convergence. We assessed convergence
visually and checked that scale reduction factors for all parameters
were less than 1.1. There were six instances where the scale reduction
factor for a particular parameter was greater than 1.1. In those cases,
we checked the traceplots of the violating parameter and discovered that
one chain, out of three, was poorly behaved. Therefore, we removed that
chain from the analysis, leaving two well-mixed and converged chains for
those six parameters. For the purposes of including parameter
uncertainty in our population models, we retained the final 1,000
iterations from each of the three MCMC chains to be used as randomly
drawn values during population simulation. We report the posterior mean,
standard deviation, and 95\% Bayesian Credible Intervals for every
parameter of each model for each species in the Supporting Information
(Tables S5-S20).

@@

For models with climate covariates, our objective is to model the
response of our focal grass species to interannual variation in climate,
even if those responses are weak. Therefore, we avoid selecting among
models with all possible combinations of climate covariates, and instead
use Bayesian ridge regression to regulate, or constrain, the posterior
distributions of each climate covariate (Gerber et al. 2015, Hooten and
Hobbs 2015). Ridge regression is a specific application of statistical
regularization that seeks to optimize model generality by trading off
bias and variance. As the name implies, statistical regularization
involves the use of a regulator that constrains an optimization. The
natural regulator in a Bayesian application is the prior on the
coefficient of interest. Each of our statistical models includes the
effects of climate covariates via the term
\(\textbf{z}'_t \boldsymbol{\beta}_c\) with prior
\(\boldsymbol{\beta}_c \sim \text{Normal}(\boldsymbol{\mu}_{\beta_c}, \sigma_{\beta_c}^2\textbf{I})\).
Because we standardized all climate covariates to have mean zero and
variance one, we set \(\boldsymbol{\mu}_{\beta_c} = 0\) and let
\(\sigma_{\beta_c}^2\) serve as the regulator that shrinks covariates
toward zero -- the smaller the prior variance, the more the posteriors
of \(\boldsymbol{\beta}_c\) are shrunk toward zero, and the stronger the
penalty (Hooten and Hobbs 2015).

@@

\vspace{-3em}\begin{align}
\sum_{t=1}^T \text{log}_e \left(\frac{1}{S} \sum^S_{s=1}(y_{t,\text{hold}}|\theta_{ts})  \right).
\end{align}\vspace{-3em}

@@

Using samples from the posterior distribution of the vital rate
statistical models, it is straightforward to simulate the population
models. We used an Integral Projection Model (IPM) to simulate
populations based on individual-level data (Ellner and Rees 2006) and a
quadrat-based version of an individually-based model (Quadrat-Based
Model, QBM) to simulate populations based on quadrat-level data. We
describe each in turn.

@@

We used random draws from the final 1,000 iterations from each of three
MCMC chains for each vital rate regression to carry-through parameter
uncertainty into our population models. At each time step, we drew the
full parameter set (climate effects and density-dependence fixed
effects) from a randomly selected MCMC iteration. Relatively unimportant
climate covariates (those that broadly overlap 0) will have little
effect on the mean of the simulation results, but can contribute to
their variation. To retain temporal variation associated with random
year effects, we used posterior estimates of the mean temporal effect
and the standard deviation of that effect to generate a random year
effect for unobserved years. That is, for some future year \emph{T}, the
intercept is
\(\beta_{0,T} \sim \text{Normal}(\beta_0, \sigma_{\beta_0})\) and the
effect of size is
\(\beta_{s,T} \sim \text{Normal}(\beta_s, \sigma_{\beta_s})\).

@@

An important feature of any forecasting model is the rate at which
forecast skill declines as the time between an observation and a
forecast increases.
\textcolor{blue}{In particular, we are interested in the temporal distance at which forecast skill falls below a threshold: the so-called ecological forecast horizon}
(Petchey et al. 2015). To assess the forecast horizons of our models, we
initiate the forecast model with the population state at some time
\emph{t} and make sequential forecasts of the population at times
\(t+1, t+2, \dots, t+T\) where \emph{T} is the maximum number of years
between the initial year and the final year of our observations. For
example, if we initialize the forecast model with percent cover in 1940,
we are able to make five forecasts up to the year 1945. Forecast models
are not re-initialized with observations between years. Thus, in our
current example, the model forecast for percent cover in 1941 has a
forecast horizon of one year, the forecast in 1942 has a forecast
horizon of two years, and so on. We performed these simulations for all
model types (IPM with/without climate; QBM with/without climate) using
mean parameter values for all possible initial years. For a given
forecast distance, we averaged the correlation between forecasts and
observations. Note that these forecasts are all made using in-sample
data because we used model fits from the full data set. Nonetheless,
these simulations offer insight into the differences among model
forecast horizons.
\textcolor{blue}{We chose a forecast accuracy of $\rho = 0.5$ as our forecast proficiency threshold.
So, the forecast horizon is the temporal distance at which forecast accuracy falls below $\rho = 0.5$.}

@@

The IPM and QBM generated one-step-ahead forecasts of similar skill for
out-of-sample observations, with an average correlation between
predictions and observations (\(\rho\)) of 0.72 across all models and
species (Fig. 2). Without climate covariates, the accuracy of forecasts
from the IPM were not statistically greater than the accuracy of
forecasts from the QBM (Fig. 2) and overall error was similar (mean
absolute error; Fig. S1, Supporting Information). With climate
covariates, the best out-of-sample predictive model (highest
\emph{lppd}) for each species and vital rate typically resulted from
highly constrained priors on the climate effects (Fig. S2, Supporting
Information). Thus, the posterior distributions of climate effects
included in our models overlapped zero and generally shrunk toward zero,
though for some species-vital rate combinations, important effects (80\%
credible interval does not include zero) did emerge (Fig. 3).

@@

With climate covariates included \textbackslash{}textcolor\{blue\{and
using mean parameter values, the accuracy of both models' forecasts
declined as the distance between the last observation and the forecast
increased\}, but they did so at similar rates (Fig. 4). The only
exception is for \emph{Poa secunda}, where QBM forecast accuracy
remained steady as the
\textcolor{blue}{temporal distance of the forecast increased}, whereas
IPM forecast accuracy declined (Fig. 4).
\textcolor{blue}{The forecast horizons were short: forecast accuracy fell below $\rho$ = 0.5 after one year for the IPM for most species, and after four years, at most, for the QBM (Fig. 4).
Across the different temporal distances from the observation to the forecast, the IPM was never more accurate than the QBM (Table S23).
Likewise, the QBM was rarely more accurate the IPM, the only exception being for \emph{H. comata} at temporal distances of two ($t_{(115)}$ = 2.39, \emph{P} = 0.002) and three years ($t_{(98)}$ = 2.04, \emph{P} = 0.022) (Table S24).
There were some cases where the QBM was more accurate than the IPM for \emph{Poa secunda}, but neither model exceeded the forecast profieciency threshold by a large margin (Fig. 4, Table S24).}

@@

Our comparison of a traditional, demographic population model without
environmental forcing (the IPM) to an equivalent model inspired by
density-structured models (the QBM) showed that, generally, IPM
forecasts of out-of-sample plant population states were no more accurate
than forecasts from the QBM (Fig. 2; `no-climate' bars). This result
overturned our expectation that the IPM would out-perform the QBM,
thanks to its mechanistic representation of the perennial life cycle,
and confirms theoretical (Freckleton et al. 2011) and empirical work
(Taylor and Hastings 2004, Queenborough et al. 2011) showing that
density-structured models can be useful surrogates for demographic
models when the goal is to estimate or forecast population states over
large spatial extents.

We also expected the inclusion of environmental forcing to reveal more
differences between the models. Interannual variation in weather can
affect vital rates in different ways (Dalgleish et al. 2011), so,
estimates of climate effects on plant population growth may be biased or
non-identifiable when the underlying statistical model is fit using
population-level data that integrates over the potentially unique
climate responses of individual vital rates. We found some evidence that
the QBM failed to detect climate effects for three species (\emph{B.
gracilis}, \emph{H. comata}, and \emph{Poa secunda}), where important
climate effects were identified in the individual vital rate models but
not in the percent cover model (Fig. 3). However, for the two species
where including climate covariates increased forecast accuracy (\emph{B.
gracilis} and \emph{Poa secunda}), forecast skill (Fig. 2) and error
(Fig. S2) were equivalent between the IPM and QBM.

The higher accuracy of the IPM and QBM with climate covariates for
\emph{B. gracilis} and \emph{Poa secunda} highlights the advantage of
contemporary modeling and variable selection approaches such as ridge
regression and LASSO over techniques that would exclude
``non-significant'' effects from final models. Ridge regression allows
researchers to retain covariates whose effects may be difficult to
identify in noisy data or short time series. This is especially
important when forecasting the impacts of climate variability, where it
is important to include to effects of forcing variables (e.g.,
temperature and precipitation) even if such effects are difficult to
identify. Indeed, we failed to detect strong climate effects in the QBM
for \emph{B. gracilis} and \emph{Poa secunda}, but including climate
covariates still improved forecasting skill (Fig. 2). If a species is
truly unresponsive to a given climate variable, statistical
regularization techniques will shrink the mean and variance of a
covariate estimate toward zero (Hooten and Hobbs 2015). Of course, no
matter what model selection approach is adopted, a critical step is
identifying the appropriate candidate covariates, which we attempted to
do based on our knowledge of this semi-arid plant community. However,
the climate covariates we chose required aggregating daily weather data
over discrete time periods. It is possible that we did not choose the
optimal time periods over which to aggregate. New methods using
functional linear models (or splines) may offer a data-driven approach
for identifying the appropriate time periods over which to aggregate to
produce a tractable set of candidate climate variables (Teller et al.
2016).

We also expected IPM forecast accuracy to decline at a lower rate than
the QBM as the
\textcolor{blue}{time between the last observation and the forecast increased.}
In principle, more mechanistic models should produce better predictions,
especially under novel conditions (Evans 2012, Schindler and Hilborn
2015). In our case, the IPM explicitly models the influence of weather
on recruitment and survival, effects that may be poorly represented in
the QBM because recruitment and survival mainly affect small plants that
contribute little to year-to-year changes in percent cover. Over time,
of course, the addition and subtraction of small plants can have large
effects on population growth, so explicitly modeling these effects could
contribute to a longer forecast horizon. However, we found no evidence
\textcolor{blue}{that the forecast horizon for the IPM was greater than the QBM (Fig. 4).
On the contrary, the QBM tended to have a slightly longer forecast horizon than the IPM for most species (Fig. 4).
The QBM has fewer processes, so may better capture near term dynamics when populations do not fluctuate widely, as in our case.
When populations do not fluctuate widely, often the best forecast for population size at \emph{t+1} is the size at time \emph{t}.
Thus, a simpler model such as the QBM may be well-suited for predicting populations that fluctuate mildly around an equilibrium.}

Our comparison of a model based on individual-level data with one based
on percent cover data is not an exhaustive test. Understanding the
reasons why the percent cover-based model matched the skill of a
demographic model for our focal species may help us anticipate
situations in which a percent-cover approach would fail. First, for none
of our species did a climate covariate have a strong negative effect on
one vital rate and a strong positive effect on a different vital rate
(Fig. 3). As noted by Freckleton et al. (2011), complex age or stage
structure can compromise predictions from models that aggregate over
life-histories, and the same should be true when aggregating across
vital rates with contrasting responses to climate drivers. Second, our
particular recruitment model is already so aggregated -- it averages
across seed production, germination and establishment -- that it may
fail to detect important demographic responses to climate, putting our
individual-based model and percent cover model on more equal footing.
More finely resolved recruitment data might help our individual-based
model outperform the population-level model. As advocated by Freckleton
et al. (2011), knowledge of a species' population ecology should guide
the modeling approach.
\textcolor{blue}{Third, our percent cover data are essentially error-free because we were able to aggregate indiviual plant areas to calculate percent cover.
Percent cover data collected by typical sampling protocals (e.g., Daubenmire frames) will include error that would affect population forecasts due to misspecifing the initial conditions and/or biasing model parameters}
(Queenborough et al. 2011).
\textcolor{blue}{Thus, it may be that our percent cover model performed just as well as the individual-based model because percent cover was perfectly measured.
One way to account for such error is to develop a sampling model that relates the observations (estimated percent cover in a plot) to the true state (percent cover derived from individual plant measurements in the same plot)}
(Hobbs and Hooten 2015).

>>>>

We compared the forecasting skill
\textcolor{blue}{(accuracy and precision)} of statistical and population
models based on aggregated, population-level data with the skill of
models based on individual-level data. We used a demographic dataset
that tracks the fates of individual plants from four species over 14
years to build two kinds of single-species population models,
traditional models using individual growth, survival, and recruitment
data and alternative models based on population-level (basal cover)
data. We simulated from the models to answer two questions motivated by
the fact that the effects of intraspecific competition (density
dependence) and interannual weather variability act at the level of the
individual (Clark et al. 2011). First, can population models fit using
aggregated individual-level data (percent cover) adequately capture
density dependence to produce forecasts as skillful as those from models
fit to demographic data? Second, can population models fit using
aggregated data adequately capture the influence of climate on
population growth and, in turn, produce forecasts as skillful as those
from models fit to demographic data?

@@

\textcolor{blue}{We used two types of data: individual-level data and percent cover data.
Using the individual-level data, we fit three vital rate regressions (survival, growth, and rectruitment) to build an Integral Projection Model (IPM) for simulating the plant populations.
Using the percent cover data we fit a simple, Gompertz population growth model, which we refer to as a quadrat-based model (QBM).
Both model types (IPM and QBM) were fit with and without climate covariates.
We used Bayesian ridge regression to weight the importance of each climate covariate.
We then performed cross-validation to assess each model's ability to predict out-of-sample data.
We compared the forecast accuracy ($\rho$, correlation between observations and predictions) and mean absolute error (MAE) between the IPM and the QBM to test our expectation that the IPM should outperform the QBM.
Lastly, we use in-sample forecasts to quantify each model's forecast horizon}
(Petchey et al. 2015).

@@

Our demographic data were obtained from a northern mixed grass prairie
at the Fort Keogh Livestock and Range Research Laboratory near Miles
City, Montana, USA (\(46^{\circ}\) 19' N, \(105^{\circ}\) 48' W). The
dataset is available on Ecological Archives\footnote{\url{http://esapubs.org/archive/ecol/E092/143/}}
(Anderson et al. 2011), and interested readers should refer to the
metadata for a complete description. The site is 800 m above sea level
and mean annual precipitation (1878-2009) is 334 mm, with most annual
precipitation falling from April through September. The community is
grass-dominated, and we focused on the four most abundant grass species:
\emph{Bouteloua gracilis} (BOGR), \emph{Hesperostipa comata} (HECO),
\emph{Pascopyrum smithii} (PASM), and \emph{Poa secunda} (POSE) (Fig. 1
and Table 1). \emph{B. gracilis} is a warm-season perennial grass,
whereas \emph{H. comata}, \emph{P. smithii}, and \emph{Poa secunda} are
cool-season perennial grasses. The growing season begins in early spring
(typically in April) and lasts through mid-summer (typically in June).

From 1932 to 1945, individual plants were identified and mapped annually
in 44 1-\(\text{m}^2\) quadrats using a pantograph. The quadrats were
distributed among six pastures, each assigned a grazing treatment of
light (1.24 ha/animal unit month), moderate (0.92 ha/aum), and heavy
(0.76 ha/aum) stocking rates (two pastures per treatment). In this
analysis, we accounted for potential differences among the grazing
treatments, but do not focus on grazing\(\times\)climate interactions.
The annual maps of the quadrats were digitized and the fates of
individual plants tracked and extracted using a computer program
(Lauenroth and Adler 2008, Chu et al. 2014). The permanent quadrats have
not been relocated, but their distribution in six different pastures
implies that the data represent a broad spatial distribution for the
study area. Daily climate data are available for the duration of the
data collection period (1932 - 1945) from the Miles City airport, Wiley
Field, 9 km from the study site.

We modeled each grass population based on two levels of data: individual
and quadrat. The individual data are the ``raw'' data. For the
quadrat-level data, we summed individual basal cover for each quadrat by
species. This is equivalent to a near-perfect census of quadrat percent
cover because measurement error at the individual-level is small (Chu
and Adler 2015). Based on these two datasets of 13 year-to-year
transitions, we can compare population models built using
individual-level data and aggregated, quadrat-level data. At the
individual level, we explicitly model three vital rates: growth,
survival, and recruitment. At the quadrat level, we model population
growth as change in percent cover of quadrats with non-zero cover in
year \emph{t} and in year \emph{t-1}, ignoring within-quadrat
extirpation and colonization events because they are very rare in our
time series (\(N=16\) and \(N=13\), respectively, across all species).
Sample sizes for each species and vital rate model are shown in Table 1.

@@

Our Bayesian approach to fitting the vital rate models required choosing
appropriate priors for unknown parameters and deciding which, if any, of
those priors should be hierarchical. For each species, we fit yearly
size effects and yearly intercepts hierarchically, where year-specific
coefficients were modeled with global distributions representing the
mean size effect and intercept. Quadrat random effects were also fit
hierarchically, with quadrat offsets modeled with distributions with
mean zero and a shared variance term (independent Gaussian priors).
Climate effects were modeled as independent covariates whose prior
distributions were optimized for prediction using statistical
regularization (see \textbf{Statistical regularization: Bayesian ridge
regression} below).

All of our analyses (model fitting and simulating) were conducted in R
(R Core Team 2013). We used the `No-U-Turn' Hamiltonian Monte Carlo
sampler in Stan (Stan Development Team 2014a) to sample from the
posterior distribution of model parameters using the package
\texttt{rstan} (Stan Development Team 2014b). We obtained samples from
the posterior distribution for all model parameters from three parallel
MCMC chains run for 1,000 iterations after discarding an initial 1,000
iterations. Such short MCMC chains are possible because the Stan sampler
reduces the number of iterations needed to achieve convergence. We
assessed convergence visually and checked that scale reduction factors
for all parameters were less than 1.1. For the purposes of including
parameter uncertainty in our population models, we retained the final
1,000 iterations from each of the three MCMC chains to be used as
randomly drawn values during population simulation. We report the
posterior mean, standard deviation, and 95\% Bayesian Credible Intervals
for every parameter of each model for each species in the Supporting
Information (Tables S5-S20).

@@

For models with climate covariates, our objective is to model the
response of our focal grass species to interannual variation in climate,
even if those responses are weak. Therefore, we avoid selecting among
models with all possible combinations of climate covariates, and instead
use Bayesian ridge regression to regulate, or constrain, the posterior
distributions of each climate covariate (Gerber et al. 2015, Hooten and
Hobbs 2015). Ridge regression is a specific application of statistical
regularization that seeks to optimize model generality by trading off
bias and variance. As the name implies, statistical regularization
involves the use of a regulator that constrains an optimization. The
natural regulator in a Bayesian application is the prior on the
coefficients of interest. Each of our statistical models includes the
effects of climate covariates via the term
\(\textbf{z}'_t \boldsymbol{\beta}_c\) with prior
\(\boldsymbol{\beta}_c \sim \text{Normal}(\boldsymbol{\mu}_{\beta_c}, \sigma_{\beta_c}^2\textbf{I})\).
Because we standardized all climate covariates to have mean zero and
variance one, we set \(\boldsymbol{\mu}_{\beta_c} = 0\) and let
\(\sigma_{\beta_c}^2\) serve as the regulator that shrinks covariate
effects toward zero -- the smaller the prior variance, the more the
posteriors of \(\boldsymbol{\beta}_c\) are shrunk toward zero, and the
stronger the penalty (Hooten and Hobbs 2015).

@@

\vspace{-3em}\begin{align}
\sum_{t=1}^T \text{log}_e \left(\frac{1}{S} \sum^S_{s=1}[y_{t,\text{hold}}|\theta_{ts}]  \right).
\end{align}\vspace{-3em}

@@

Using samples from the posterior distribution of the vital rate
statistical models, it is straightforward to simulate the population
models. We used an Integral Projection Model (IPM) to simulate
populations based on individual-level data (Ellner and Rees 2006) and a
quadrat-based version of an individually-based model (Quadrat-Based
Model, QBM) to simulate populations based on quadrat-level data. We
describe each in what follows.

@@

We used random draws from the final 1,000 iterations from each of three
MCMC chains for each vital rate regression to carry-through parameter
uncertainty into our population models. At each time step, we drew the
full parameter set (climate effects and density-dependence fixed
effects) from a randomly selected MCMC iteration. Relatively unimportant
climate covariates (those that broadly overlap 0) will have little
effect on the mean of the simulation results, but can contribute to
their variation. To retain temporal variation associated with random
year effects, we used posterior estimates of the mean temporal effect
and the standard deviation of that effect to generate a random year
effect for unobserved years. That is, for some future year \emph{T}, the
intercept is
\(\beta_{0,T} \sim \text{Normal}(\beta_0, \sigma_{\beta_0}^2)\) and the
effect of size is
\(\beta_{s,T} \sim \text{Normal}(\beta_s, \sigma_{\beta_s}^2)\).

@@

An important feature of any forecasting model is the rate at which
forecast skill declines as the time between an observation and a
forecast increases.
\textcolor{blue}{In particular, we are interested in the temporal distance at which forecast skill falls below a threshold: the so-called ecological forecast horizon}
(Petchey et al. 2015). To assess the forecast horizons of our models, we
initiate the forecast model with the population state at some time
\emph{t} and make sequential forecasts of the population at times
\(t+1, t+2, \dots, t+T\) where \emph{T} is the maximum number of years
between the initial year and the final year of our observations. For
example, if we initialize the forecast model with percent cover in 1940,
we are able to make five forecasts up to the year 1945. Forecast models
are not re-initialized with observations between years. Thus, in our
current example, the model forecast for percent cover in 1941 has a
forecast horizon of one year, the forecast in 1942 has a forecast
horizon of two years, and so on. We performed these simulations for all
model types (IPM with/without climate; QBM with/without climate) using
mean parameter values for all possible initial years. For a given
forecast distance, we averaged the correlation between forecasts and
observations. Note that our forecasts for the horizon analysis are all
made using in-sample data because we used model fits from the full data
set. Nonetheless, our simulations offer insight into the differences
among model forecast horizons.
\textcolor{blue}{We chose a forecast accuracy of $\rho = 0.5$ as our forecast proficiency threshold.
So, the forecast horizon is the temporal distance at which forecast accuracy falls below $\rho = 0.5$.}

@@

The IPM and QBM generated one-step-ahead forecasts of similar skill for
out-of-sample observations, with an average correlation between
predictions and observations (\(\rho\)) of 0.72 across all models and
species (Fig. 2). Without climate covariates, the accuracy of forecasts
from the IPM were not statistically greater than the accuracy of
forecasts from the QBM (Fig. 2) and overall error was similar (mean
absolute error; Fig. S1, Supporting Information). With climate
covariates, the best out-of-sample predictive model (highest
\emph{lppd}) for each species and vital rate typically resulted from
highly constrained priors on the climate effects (Fig. S2, Supporting
Information). Thus, the posterior distributions of climate effects
included in our models overlapped zero and generally were shrunk toward
zero, though for some species-vital rate combinations, important effects
(80\% credible interval does not include zero) did emerge (Fig. 3).

@@

With climate covariates included
\textcolor{blue}{and using mean parameter values, the accuracy of both models' forecasts declined as the distance between the last observation and the forecast increased},
but they did so at similar rates (Fig. 4). The only exception is for
\emph{Poa secunda}, where QBM forecast accuracy remained steady as the
\textcolor{blue}{temporal distance of the forecast increased}, whereas
IPM forecast accuracy declined (Fig. 4).
\textcolor{blue}{The forecast horizons were short: forecast accuracy fell below $\rho$ = 0.5 after one year for the IPM for most species, and after four years, at most, for the QBM (Fig. 4).
Across the different temporal distances from the observation to the forecast, the IPM was never more accurate than the QBM (Table S23).
Likewise, the QBM was rarely more accurate the IPM, the only exception being for \emph{H. comata} at temporal distances of two ($t_{(115)}$ = 2.39, \emph{P} = 0.002) and three years ($t_{(98)}$ = 2.04, \emph{P} = 0.022) (Table S24).
There were some cases where the QBM was more accurate than the IPM for \emph{Poa secunda}, but neither model exceeded the forecast profieciency threshold by a large margin (Fig. 4, Table S24).}

@@

Our comparison of a traditional, demographic population model without
environmental forcing (the IPM) to an equivalent model inspired by
density-structured models (the QBM) showed that, generally, IPM
forecasts of out-of-sample plant population states were no more accurate
than forecasts from the QBM (Fig. 2; `no-climate' bars). This result
differed from our expectation that the IPM would out-perform the QBM,
because of its mechanistic representation of the perennial life cycle.
Our result also confirms theoretical (Freckleton et al. 2011) and
empirical work (Taylor and Hastings 2004, Queenborough et al. 2011)
showing that density-structured models can be useful surrogates for
demographic models when the goal is to estimate or forecast population
states over large spatial extents.

We also expected the inclusion of environmental forcing to reveal more
differences between the models. Interannual variation in weather can
affect vital rates in different ways (Dalgleish et al. 2011). Thus,
estimates of climate effects on plant population growth may be biased or
non-identifiable when the underlying statistical model is fit using
population-level data that integrates over the potentially unique
climate responses of individual vital rates. We found some evidence that
the QBM failed to detect climate effects for three species (\emph{B.
gracilis}, \emph{H. comata}, and \emph{Poa secunda}), where important
climate effects were identified in the individual vital rate models but
not in the percent cover model (Fig. 3). However, for the two species
where including climate covariates increased forecast accuracy (\emph{B.
gracilis} and \emph{Poa secunda}), forecast skill (Fig. 2) and error
(Fig. S2) were equivalent between the IPM and QBM.

The higher accuracy of the IPM and QBM with climate covariates for
\emph{B. gracilis} and \emph{Poa secunda} highlights the advantage of
contemporary modeling and variable selection approaches such as ridge
regression and LASSO over techniques that would exclude
``non-significant'' effects from final models. Ridge regression allows
researchers to retain covariates whose effects may be difficult to
identify in noisy data or short time series. This is especially
important when forecasting the impacts of climate variability, where it
is important to include the effects of forcing variables (e.g.,
temperature and precipitation) even if such effects are difficult to
identify. Indeed, we failed to detect strong climate effects in the QBM
for \emph{B. gracilis} and \emph{Poa secunda}, but including climate
covariates still improved forecasting skill (Fig. 2). If a species is
truly unresponsive to a given climate variable, statistical
regularization techniques will shrink the mean and variance of a
covariate estimate toward zero (Hooten and Hobbs 2015). Of course,
regardless of what model selection approach is adopted, a critical step
is identifying the appropriate candidate covariates, which we attempted
to do based on our knowledge of this semi-arid plant community. However,
the climate covariates we chose required aggregating daily weather data
over discrete time periods. It is possible that we did not choose the
optimal time periods over which to aggregate. New methods using
functional linear models (or splines) may offer a data-driven approach
for identifying the appropriate time periods over which to aggregate to
produce a tractable set of candidate climate variables (Sims et al.
2007, Pol and Cockburn 2011, Teller et al. 2016).

We also expected IPM forecast accuracy to decline at a lower rate than
the QBM as the
\textcolor{blue}{time between the last observation and the forecast increased.}
In principle, more mechanistic models should produce better predictions,
especially under novel conditions (Evans 2012, Schindler and Hilborn
2015). In our case, the IPM explicitly models the influence of weather
on recruitment and survival, effects that may be poorly represented in
the QBM because recruitment and survival mainly affect small plants that
contribute little to year-to-year changes in percent cover. Over time,
the addition and subtraction of small plants can have large effects on
population growth, thus, explicitly modeling these effects could
contribute to a longer forecast horizon. However, we found no evidence
\textcolor{blue}{that the forecast horizon for the IPM was greater than the QBM (Fig. 4).
On the contrary, the QBM tended to have a slightly longer forecast horizon than the IPM for most species (Fig. 4).
The QBM has fewer processes, thus it may better capture near term dynamics when populations do not fluctuate widely, as in our case.
When populations do not fluctuate widely, often the best forecast for population size at \emph{t+1} is the size at time \emph{t}.
Thus, a simpler model such as the QBM may be well-suited for predicting populations that fluctuate mildly around an equilibrium.}

Our comparison of a model based on individual-level data with one based
on percent cover data is not an exhaustive test. Understanding the
reasons why the percent cover-based model matched the skill of a
demographic model for our focal species may help us anticipate
situations in which a percent-cover approach would fail. First, for none
of our species did a climate covariate have a strong negative effect on
one vital rate and a strong positive effect on a different vital rate
(Fig. 3). As noted by Freckleton et al. (2011), complex age or stage
structure can compromise predictions from models that aggregate over
life-histories, and the same should be true when aggregating across
vital rates with contrasting responses to climate drivers. Second, our
particular recruitment model is already so aggregated -- it averages
across seed production, germination and establishment -- that it may
fail to detect important demographic responses to climate, putting our
individual-based model and percent cover model on more equal footing.
More finely resolved recruitment data might help our individual-based
model outperform the population-level model. As advocated by Freckleton
et al. (2011), knowledge of a species' population ecology should guide
the modeling approach.
\textcolor{blue}{Third, our percent cover data are essentially error-free because we were able to aggregate indiviual plant areas to calculate percent cover.
Percent cover data collected by typical sampling protocals (e.g., Daubenmire frames) will include error that may affect population forecasts due to misspecifing the initial conditions and/or biasing model parameters}
(Queenborough et al. 2011).
\textcolor{blue}{Thus, it may be that our percent cover model performed just as well as the individual-based model because percent cover was perfectly measured.
One way to account for such error is to develop a sampling model that relates the observations (estimated percent cover in a plot) to the true state (percent cover derived from individual plant measurements in the same plot)}
(Hobbs and Hooten 2015).

\textcolor{blue}{Although our main goal was to compare individual-based and population-level modeling approaches relative to one another, it is worth reflecting on the absolute forecasting skill of our models.
In particular, the forecast horizon of both models, defined as the time horizon at which the correlation between predictions and observations falls below $\rho = 0.5$, is less than five years for all species. 
Such short forecast horizons are not encouraging.}
\textcolor{blue}{Unfortunately, we have little to offer on how to improve population forecasts that has not already been proposed}
(Mouquet et al. 2015, Petchey et al. 2015).
\textcolor{blue}{Longer time-series should improve our ability to detect exogenous drivers such as climate}
(Teller et al. 2016),
\textcolor{blue}{and modeling larger spatial extents may reduce parameter uncertainty}
(Petchey et al. 2015).
\textcolor{blue}{We may also have to shift our perspective from making explicit point forecasts to making moving average forecasts}
(Petchey et al. 2015).
\textcolor{blue}{For example, IPMs are typically capable of estimating equilibrium abundances}
(e.g., Adler et al. 2012),
\textcolor{blue}{which may be more appropriate for dynamic systems.}
